### 2021-07-11 doc/thesis/chapters/implementation.tex
new diagram

\includepicture [1.0] [0] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/bd_detailed_dsp}

@@

  \item \textbf{FM Demodulator}\\
      The FM demodulator is implemented as a Baseband Delay Modulator, as described in \ref{sec:BasebandDelayDemodulator}.

@@

Several of the listed details are implemented, in order to achieve a successful demodulation of the FM signal.

>>>>

\includepicture [1.0] [0] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/draw.io/bd_dsp_detailed}

@@

  \item \textbf{FM Demodulator}\\
      The FM demodulator is implemented as a Baseband Delay Modulator, as described in Section \ref{sec:BasebandDelayDemodulator}.

@@

\noindent
Several of the listed details are implemented, in order to achieve a successful demodulation of the FM signal.
